The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
incorporating case study indiv fitness perspective

For instance, social scale is major consideration for social network analysis,
especially in the context of different types of relationships, such as grooming
and association, that are typically examined separately while answering a single
question [@Castles_2014; @Cater_2015; @Farine_2015a]. Furthermore, it is a
common trope that individuals must be associating to interact, and many studies
therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
instance, baboons need to be in proximity in order to groom each other. However,
animals have certain interactions that do not require proximity such as
long-distance vocalization and olfactory signals [@Carter_2015] With the
advancement of biologging technology, we have the ability to record social
interactions that do not require proximity, particularly long-distance
communication networks with devices like microphone arrays [Snijders_2017].
These varying social scales can have different fitness repercussions for
individuals. Rhesus macaques (*Macaca mulatta*) had higher survivorship when
they had fewer but stronger, more stable social associates and grooming partners
rather than simply more associates [Ellis_2019]. This finding highlights that
different qualities of social scales have lasting consequences.

Temporal scale is also important for understanding the repercussions of social
phenotypes. For instance, social phenotypes can change over ontogeny in ways
that can affect fitness [@Berger_2015, @Brent_2017]. Thus, it is critical to
carefully consider the temporal scale that is meaningful for the proposed
hypotheses. Further complicating the issue of selecting suitable time scales
across ontogeny, individuals progress through development at different rates
[@Tarka_2018]. This variation can make defining appropriate temporal scales for
testing the fitness implications of an individual’s social phenotype over
different stages of ontogeny even more difficult when they vary by individual.
However, considering fine temporal scales provide insight across developmental
stages that may otherwise be missed [@Turner_2018].

@@

On the other hand, picking the proper temporal scale is important but a
challenge because all layers in the multilayer network should reflect the same
time period, and the period should be long enough for each layer to have enough
data for robust networks [@Farine_2017]. These considerations may be limiting
factors when answering questions that require timeframes that are relevant to
different individuals, for instance. In both mono- and multilayer networks, the
effect of scale on the relationship between an individual’s social network
position and fitness need to be considered based on the hypotheses being tested
and logistical constraints.

>>>>

For instance, social scale is major consideration for social network analysis,
especially in the context of different types of relationships, such as grooming
and association, that are typically examined separately while answering a single
question [@Castles_2014; @Carter_2015; @Farine_2015a]. Furthermore, it is a
common trope that individuals must be associating to interact, and many studies
therefore assume that proximity is proxy for interacting [@Farine_2015a]. For
instance, baboons need to be in proximity to groom each other. However, animals
have certain interactions that do not require proximity such as long-distance
vocalization and olfactory signals [@Carter_2015] With the advancement of
biologging technology, we have the ability to record social interactions that do
not require proximity, particularly long-distance communication networks with
devices like microphone arrays [@Snijders_2017]. Using relocation data, our case
study results indicate that there are different social patterns in different
habitat types, likely indicating different types of interactions. When the
social threshold is greater than approximately 50 m during the summer **check**,
individuals demonstrate dramatically different graph strength **cite spatial threshold fig** 
in different habitat types, having dramatically higher graph
strength in forage and open habitats than forest where they can likely see each
other better and still interact with visual cues. Varying social scales can have
different fitness repercussions for individuals. Rhesus macaques (*Macaca mulatta*) 
had higher survivorship when they had fewer but stronger, more stable
social associates and grooming partners rather than simply more associates
[@Ellis_2019]. This finding highlights that different qualities of social scales
have lasting consequences.

Temporal scale is also important for understanding the repercussions of social
phenotypes. Varying the time window length and position for caribou, we found
there was a lot of variation in the multilayer network metrics **cite winpos and winlen**. 
These changes in the outcome depending on how the time window is
defined highlight how critical it is to properly define the time window
appropriately to address the questions and hypotheses of interest. For instance,
social phenotypes can change over ontogeny in ways that can affect fitness
[@Berger_2015, @Brent_2017]. Thus, it is critical to carefully consider the
temporal scale that is meaningful for the proposed hypotheses. Further
complicating the issue of selecting suitable time scales across ontogeny,
individuals progress through development at different rates [@Tarka_2018]. This
variation can make defining appropriate temporal scales for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny even more difficult when they vary by individual. However, considering
fine temporal scales provide insight across developmental stages that may
otherwise be missed [@Turner_2018].

@@

Conversely, picking the proper temporal scale is important but a challenge
because all layers in the multilayer network should reflect the same time
period, and the period should be long enough for each layer to have enough data
for robust networks [@Farine_2017]. These considerations may be limiting factors
when answering questions that require timeframes that are relevant to different
individuals, for instance. In both mono- and multilayer networks, the effect of
scale on the relationship between an individual’s social network position and
fitness need to be considered based on the hypotheses being tested and
logistical constraints.
